---
title: "Data Visualization Demo"
date: "4/9/2021"
output: 
  html_notebook:
    toc: TRUE 
    toc_depth: 3
    toc_float: 
      collapsed: true 
      smooth_scroll: false 
    number_sections: false 
    fig_caption: true 
    code_folding: hide  
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}
library(ggplot2)
library(tidyverse)
```

```{r,echo=FALSE, message=FALSE}
setwd("C:/Users/cleon/OneDrive/Data Visualization/Data_Viz_Practice")
```

```{r, echo=FALSE, message=FALSE}
df <- read.csv("../data/hate-crimes/hate_crimes.csv")
```


# Introduction

As a fun practice I thought I would create various visualizations, from basic to advanced, as practice and a good refresher example to refer back to. My intent is to first create these visualizations using the ggplot package and then try to replicate them with other packages. 

# Scatterplot {.tabset}

**Method Reflection**

## GGPlot 

```{r}
gg_scatter <-  ggplot(df, aes(x=median_household_income, y = avg_hatecrimes_per_100k_fbi)) + 
                geom_point()
gg_scatter
```


## Plotly 

## Matplotlib 

# Bar Chart {.tabset}

## GGPlot

## Plotly 

## Matplotlib 

# Histogram {.tabset}

## GGPlot

## Plotly 

## Matplotlib 

# Resources

* GGPlot Cheat Sheet 
* https://github.com/fivethirtyeight/data 
